Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-05-15 revision-final/paper.tex
emphasis to emphasize
relative to comparable

   \item Scaling to maximum 1 (but leaving the minimum unchanged) can help
  emphasis the relative shape.

@@

Note that the use of local scales needs to be clearly marked. The viewer must realize that the scale is not relative and that big patterns in some locations might be just tiny, nugatory effects. To indicate this on the locally scaled data plots, one can use an additional aesthetic, like color, to encode the range of original scale. This is illustrated in Figure~\ref{fig:scaling-col}. In the encoding, emphasis is placed on the locations with larger range, stronger effects: the line intensity is darker (left plot), and the background is lightened to provide greater contrast (right plot) drawing the eye to these regions.

>>>>

   \item Scaling to maximum of 1 (but leaving the minimum unchanged) can help
  emphasize the relative shape.

@@

Note that the use of local scales needs to be clearly marked. The viewer must realize that the size is not comparable and that big patterns in some locations might be just tiny, nugatory effects. To indicate this on the locally scaled data plots, one can use an additional aesthetic, like color, to encode the range of original scale. This is illustrated in Figure~\ref{fig:scaling-col}. In the encoding, emphasis is placed on the locations with larger range, stronger effects: the line intensity is darker (left plot), and the background is lightened to provide greater contrast (right plot) drawing the eye to these regions.
